Weakly Nonlinear Analysis of the Standard and Helical Magnetorotational Instabilities in a Taylor Couette Flow

### 2016-07-15 paper/mri_paper.tex
added streamfunc plots to thingap paper
caption for parameter space plot

\begin{figure*}[h!]
\centering
\includegraphics[trim=0cm 1cm 0cm 5cm, scale=0.45]{allorders_velocity.eps}
\caption{First order (left) and second order (right) velocity perturbations. Streamlines represent velocity in the vertical-radial plane, where thicker streamlines correspond to faster speeds. The colorbar represents azimuthal velocity.}\label{allorders_velocity}
\end{figure*}

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.45]{allorders_Bfield.eps}
\caption{First order (left) and second order (right) magnetic field perturbations. Streamlines represent velocity in the vertical-radial plane, where thicker streamlines correspond to higher magnetic field strengths. The colorbar represents azimuthal magnetic field strength.}\label{allorders_Bfield}
\end{figure*}

>>>>

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/thingap_streamfuncs_velocity.png}%{allorders_velocity.eps}
\caption{First order (left), second order (center), and total (right) velocity perturbations. Streamlines represent velocity in the vertical-radial plane, where thicker streamlines correspond to faster speeds. Colorbar represents azimuthal velocity.}\label{allorders_velocity}
\end{figure*}

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/thingap_streamfuncs_Bfield.png}
\caption{First order (left), second order (center), and total (right) magnetic field perturbations. Streamlines represent velocity in the vertical-radial plane, where thicker streamlines correspond to higher magnetic field strengths. Colorbar represents azimuthal magnetic field strength.}\label{allorders_Bfield}
\end{figure*}

### 2016-07-15 paper/widegap_mri_paper.tex
parameter space figure added to widegap paper
changed widegap paper to twocolumn format bc we need that for apj....right?
caption for parameter space plot

\documentclass[onecolumn]{emulateapj}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\hyd}    {{\rm H}}
\newcommand{\vobs}{v_{\rm obs}}
\newcommand{\hi}{H{\sc i}~}
\newcommand{\hii}{H{\sc ii}~}
\newcommand{\hia}{H{\sc i}}
\newcommand{\hiia}{H{\sc ii}}

@@

\begin{table}[ht]
\normalsize
\caption{Fiducial parameters for MRI runs} \label{table:parameters}
\centering
%\resizebox{\textwidth}{!}
{\begin{tabular}{rlrrrrrrr}
  \hline
 & $\xi$ & $Pm$ & $\beta$ & $\Omega_2/\Omega_1$ & $R_1/R_2$ & radial magnetic b.c. \\ 
  \hline\hline
Standard MRI & 0 & 1E-3 & 25 & 0.18 & 0.33 & conducting \\ 
Helical MRI & 4 & 1E-6 & 1.7E-2 & 0.27 & 0.5 & insulating\\ 
   \hline
\end{tabular}}
\end{table}

@@

\begin{align}
& \partial_t \uphi + \frac{1}{r^2} u_0 \partial_z \Psi + \frac{1}{r} \partial_r u_0 \partial_z \Psi - \frac{2}{\beta} B_0 \partial_z B_\phi - \frac{1}{\reye} ( \nabla^2 \uphi - \frac{1}{r^2} \uphi ) = \frac{2}{\beta} \frac{1}{r} J(A, B_\phi) - \frac{1}{r} J(\Psi, \uphi) + \frac{2}{\beta}\frac{1}{r^2} B_\phi \partial_z A - \frac{1}{r^2} \uphi \partial_z \Psi \label{eq:uphi_perturbed} \\
& \partial_t A - B_0 \partial_z \Psi - \frac{1}{\reym} ( \nabla^2 A - \frac{2}{r} \partial_r A )= \frac{1}{r} J(A, \psi)  \label{eq:A_perturbed}\\
  \label{eq:Bphi_perturbed}
& \partial_t B_\phi + \frac{1}{r^2} u_0 \partial_z A - B_0 \partial_z u_\phi - \frac{1}{r} \partial_r u_0 \partial_z A - \frac{2}{r^3} B_0 \xi \partial_z \Psi - \frac{1}{\reym} (\nabla^2 B_\phi - \frac{1}{r^2} B_\phi ) = \frac{1}{r} J(A, \uphi) + \frac{1}{r} J(B_\phi, \psi)
+ \frac{1}{r^2} B_\phi \partial_z \psi - \frac{1}{r^2} \uphi \partial_z A 
\end{align}

@@

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../python/widegap/figures/orders_1_2_widegap_fiducial_eigenfunctions.pdf}
\caption{Eigenfunctions of the first order equations, first order adjoint homogenous equations, and second order equations. We use our fiducial parameters for the standard MRI ($\xi = 0$). Eigenfunctions are normalized such that either the real or imaginary part is zero.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../python/widegap/figures/nonlinear_2_3_widegap_fiducial_eigenfunctions.pdf}
\caption{Nonlinear terms $N_2$ and $N_3$ for our fiducial standard MRI parameters.}
\end{figure}

>>>>

%\documentclass[onecolumn]{emulateapj}
\documentclass{emulateapj}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\hyd}    {{\rm H}}
\newcommand{\vobs}{v_{\rm obs}}
\newcommand{\hi}{H{\sc i}~}
\newcommand{\hii}{H{\sc ii}~}
\newcommand{\hia}{H{\sc i}}
\newcommand{\hiia}{H{\sc ii}}

@@

\begin{widetext}
\begin{table*}[ht]
\normalsize
\caption{Fiducial parameters for MRI runs} \label{table:parameters}
\centering
%\resizebox{\textwidth}{!}
{\begin{tabular}{rlrrrrrrr}
  \hline
 & $\xi$ & $Pm$ & $\beta$ & $\Omega_2/\Omega_1$ & $R_1/R_2$ & radial magnetic b.c. \\ 
  \hline\hline
Standard MRI & 0 & 1E-3 & 25 & 0.18 & 0.33 & conducting \\ 
Helical MRI & 4 & 1E-6 & 1.7E-2 & 0.27 & 0.5 & insulating\\ 
   \hline
\end{tabular}}
\end{table*}

@@

\begin{align}
& \partial_t \uphi + \frac{1}{r^2} u_0 \partial_z \Psi + \frac{1}{r} \partial_r u_0 \partial_z \Psi - \frac{2}{\beta} B_0 \partial_z B_\phi - \frac{1}{\reye} ( \nabla^2 \uphi - \frac{1}{r^2} \uphi ) = \frac{2}{\beta} \frac{1}{r} J(A, B_\phi) - \frac{1}{r} J(\Psi, \uphi) + \frac{2}{\beta}\frac{1}{r^2} B_\phi \partial_z A - \frac{1}{r^2} \uphi \partial_z \Psi \label{eq:uphi_perturbed} \\
& \partial_t A - B_0 \partial_z \Psi - \frac{1}{\reym} ( \nabla^2 A - \frac{2}{r} \partial_r A )= \frac{1}{r} J(A, \psi)  \label{eq:A_perturbed}\\
  \label{eq:Bphi_perturbed}
& \partial_t B_\phi + \frac{1}{r^2} u_0 \partial_z A - B_0 \partial_z u_\phi - \frac{1}{r} \partial_r u_0 \partial_z A - \frac{2}{r^3} B_0 \xi \partial_z \Psi - \frac{1}{\reym} (\nabla^2 B_\phi - \frac{1}{r^2} B_\phi ) = \frac{1}{r} J(A, \uphi) + \frac{1}{r} J(B_\phi, \psi)
+ \frac{1}{r^2} B_\phi \partial_z \psi - \frac{1}{r^2} \uphi \partial_z A 
\end{align}
\end{widetext}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../figures/widegap_paramspace_crit_params_Pm_1E-3}
\caption{Growth rates in the ($\reym, k_z$) plane. Color map shows growth rate found by solving the linear eigenvalue problem for each ($\reym, k_z$) in the grid. The eigenvalue problem was solved for the widegap parameters listed in Table \ref{table:parameters}. Overlaid contours show growth rates at [-2E-3, -1E-3, -1E-5, 1E-5, 1E-3, 2E-3], where dashed contours represent negative values. The gray dotted line shows the interpolated marginal stability curve. The critical parameters $\reym_c = 0.84$ and $k_c = 0.0127$ correspond to the smallest parameter values that yield a zero growth rate.}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../python/widegap/figures/orders_1_2_widegap_fiducial_eigenfunctions.pdf}
\caption{Eigenfunctions of the first order equations, first order adjoint homogenous equations, and second order equations. We use our fiducial parameters for the standard MRI ($\xi = 0$). Eigenfunctions are normalized such that either the real or imaginary part is zero.}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../python/widegap/figures/nonlinear_2_3_widegap_fiducial_eigenfunctions.pdf}
\caption{Nonlinear terms $N_2$ and $N_3$ for our fiducial standard MRI parameters.}
\end{figure*}
